Explore the SingleR results

### 2025-12-18 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
Spelling updates for #1276
NBAltas -> NBAtlas

label_map_df |>
  dplyr::group_by(label_recoded) |>
  dplyr::summarize(all_labels = paste(label, collapse = ", ")) |>
  dplyr::arrange(label_recoded) |>
  dplyr::rename(
    "Label shown in figures" = label_recoded,
    "Underlying NBAltas label(s)" = all_labels
  )
```

@@

PDX samples have, not unexpectedly, much less cell type diversity overall with most cells being tumor or similar and immune cells rarely present.
This is consistent with expectations in general for the biology of PDX samples.

>>>>

label_map_df |>
  dplyr::group_by(label_recoded) |>
  dplyr::summarize(all_labels = paste(label, collapse = ", ")) |>
  dplyr::arrange(label_recoded) |>
  dplyr::rename(
    "Label shown in figures" = label_recoded,
    "Underlying NBAtlas label(s)" = all_labels
  )
```

@@

PDX samples have, not unexpectedly, much less cell type diversity overall with most cells being tumor or similar and immune cells rarely present.
This is consistent with expectations in general for the biology of xenografts.
